\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\title{Project Charter: Aurora Interactive Website}
\author{Prepared by Tanvir Sadi}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Project Overview}
\subsection{Project Basics}
\begin{itemize}[leftmargin=*]
  \item Project Name: Aurora Interactive Website
  \item Charter Version: 1.1
  \item Project Owner: Tanvir Sadi
  \item Current Phase: Planning and design baseline
  \item Target MVP Release: 2026-03-20
\end{itemize}

\subsection{Background}
This project delivers a single-page animated web experience. A user clicks one button to transition the page into a night sky and start a northern-lights animation.

\subsection{Problem Statement}
Most static pages provide limited user engagement. The project requires a lightweight, accessible, and performant animation experience that can be delivered as a frontend-only MVP.

\subsection{Vision Statement}
Deliver a fast and accessible one-click aurora website that feels immersive on desktop and mobile.

\section{Current Status and Decision Log}
\begin{itemize}[leftmargin=*]
  \item SDLC document structure is created in \texttt{latex/sdlc}.
  \item Project direction is confirmed as frontend-only MVP.
  \item Technology decision for v1 is finalized: \textbf{Vanilla HTML, CSS, and JavaScript}.
  \item No animation library is required for v1 unless performance or quality targets fail.
\end{itemize}

\section{Objectives and Success Criteria}
\subsection{Objectives}
\begin{enumerate}[leftmargin=*]
  \item Implement one-click activation for night mode and aurora animation.
  \item Deliver responsive UI for desktop and mobile.
  \item Meet accessibility and performance baseline targets.
  \item Keep SDLC documents synchronized with implementation.
\end{enumerate}

\subsection{Success Metrics}
\begin{longtable}{|p{0.30\linewidth}|p{0.20\linewidth}|p{0.40\linewidth}|}
\hline
Metric & Target & Measurement \\
\hline
Performance score & Lighthouse >= 85 & Lighthouse run on production build \\
\hline
Accessibility score & Lighthouse >= 90 & Keyboard checks plus Lighthouse \\
\hline
Interaction latency & <= 200 ms & DevTools timing from click to transition start \\
\hline
Animation smoothness & 55+ FPS desktop, 30+ FPS mobile & Browser performance profile \\
\hline
\end{longtable}

\section{Scope}
\subsection{In Scope}
\begin{itemize}[leftmargin=*]
  \item Single-page layout with one primary action button.
  \item Night-sky background transition.
  \item Northern-lights animation in the active mode.
  \item Reduced-motion fallback behavior.
  \item Responsive behavior for common mobile and desktop sizes.
\end{itemize}

\subsection{Out of Scope}
\begin{itemize}[leftmargin=*]
  \item Backend APIs and user accounts.
  \item CMS features.
  \item Native mobile apps.
  \item Real-time geolocation or weather-driven aurora model.
\end{itemize}

\section{Constraints and Assumptions}
\begin{itemize}[leftmargin=*]
  \item Budget is minimal and project is individually owned.
  \item Target browsers: latest Chrome, Edge, Firefox.
  \item Deployment will be static hosting.
  \item Modern browser features are available.
\end{itemize}

\section{Milestones}
\begin{longtable}{|p{0.34\linewidth}|p{0.18\linewidth}|p{0.38\linewidth}|}
\hline
Milestone & Date & Exit Criteria \\
\hline
Requirements and design baseline complete & 2026-02-24 & PRD, SRS, SDS first pass approved \\
\hline
Core implementation complete & 2026-03-07 & Night mode and aurora behavior implemented \\
\hline
Test and quality gate complete & 2026-03-14 & Test plan/cases executed and RTM updated \\
\hline
MVP release complete & 2026-03-20 & Deployment and release checklist passed \\
\hline
\end{longtable}

\section{Initial Risks}
\begin{itemize}[leftmargin=*]
  \item Performance drop on low-end devices.
  \item Browser rendering differences.
  \item Timeline slip due to animation tuning.
\end{itemize}

\section{Approval}
\begin{itemize}[leftmargin=*]
  \item Product Owner: Tanvir Sadi (Approved on 2026-02-18)
  \item Reviewer: TBD
\end{itemize}

\end{document}
