\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\title{Project Plan: Aurora Interactive Website}
\author{Project Team}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Plan Baseline}
\begin{itemize}[leftmargin=*]
  \item Lifecycle Model: Iterative mini-milestones (weekly checkpoints).
  \item Delivery Strategy: MVP first, then polish in controlled increments.
  \item Technology Baseline: Vanilla HTML/CSS/JS for v1.
\end{itemize}

\section{Work Breakdown Structure}
\begin{longtable}{|p{0.10\linewidth}|p{0.52\linewidth}|p{0.14\linewidth}|p{0.14\linewidth}|}
\hline
ID & Work Package & Owner & Status \\
\hline
WP-01 & Finalize requirements and UX intent & Tanvir & Completed (FR/NFR locked) \\
\hline
WP-02 & Build page structure and base styling & Tanvir & Completed \\
\hline
WP-03 & Implement night-sky transition behavior & Tanvir & Completed \\
\hline
WP-04 & Implement aurora animation loop in vanilla JS & Tanvir & Completed \\
\hline
WP-05 & Add responsive and reduced-motion behavior & Tanvir & Completed \\
\hline
WP-06 & Execute testing and update RTM & Tanvir & Completed (TC-01 to TC-10 passed) \\
\hline
WP-07 & Deploy MVP and publish release notes & Tanvir & Planned \\
\hline
\end{longtable}

\section{Schedule}
\begin{longtable}{|p{0.32\linewidth}|p{0.20\linewidth}|p{0.36\linewidth}|}
\hline
Activity Window & Date Range & Output \\
\hline
Planning and specification & 2026-02-18 to 2026-02-24 & Updated charter, plan, PRD, SRS, SDS \\
\hline
Implementation sprint 1 & 2026-02-25 to 2026-03-02 & Button trigger and night-mode transition \\
\hline
Implementation sprint 2 & 2026-03-03 to 2026-03-07 & Aurora animation and interaction polish \\
\hline
QA and hardening & 2026-03-08 to 2026-03-14 & Test evidence, accessibility and performance checks \\
\hline
Release preparation and go-live & 2026-03-15 to 2026-03-20 & Deployment and release checklist complete \\
\hline
\end{longtable}

\section{Resource Plan}
\begin{itemize}[leftmargin=*]
  \item Primary resource: Tanvir Sadi (development, QA, documentation).
  \item Optional reviewer support for UX and acceptance sign-off.
\end{itemize}

\section{Risk and Mitigation Plan}
\begin{longtable}{|p{0.10\linewidth}|p{0.34\linewidth}|p{0.44\linewidth}|}
\hline
Risk ID & Risk & Mitigation \\
\hline
R-01 & Animation performance below target & Use simpler layers, lower particle/detail count, reduced-motion mode \\
\hline
R-02 & Visual mismatch across browsers & Maintain browser matrix and fallback CSS behavior \\
\hline
R-03 & Scope expansion & Enforce MVP scope freeze after 2026-02-24 baseline \\
\hline
\end{longtable}

\section{Communication Plan}
\begin{itemize}[leftmargin=*]
  \item Weekly internal status update.
  \item Milestone completion summary in SDLC documents.
  \item Release note for go-live milestone.
\end{itemize}

\end{document}






