\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\title{Product Requirements Document (PRD): Aurora}
\author{Project Team}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Product Summary}
Aurora is a single-page interactive website. A user activates a button to transform the page into a night sky and run a northern-lights animation.

\section{Product Goals}
\begin{itemize}[leftmargin=*]
  \item Create a memorable visual interaction in one click.
  \item Keep the experience smooth and responsive.
  \item Maintain accessibility as a first-class requirement.
\end{itemize}

\section{Target Users}
\begin{itemize}[leftmargin=*]
  \item Portfolio viewers and demo audiences.
  \item Users browsing from desktop or mobile devices.
\end{itemize}

\section{User Stories}
\begin{itemize}[leftmargin=*]
  \item As a visitor, I want a clear call-to-action button so I can start the experience immediately.
  \item As a visitor, I want a smooth transition to night mode so the interaction feels polished.
  \item As a visitor, I want aurora animation that does not lag on my device.
  \item As a keyboard user, I want to trigger the same behavior without a mouse.
  \item As a motion-sensitive user, I want reduced animation when my system preference requests it.
\end{itemize}

\section{Functional Requirements}
\begin{longtable}{|p{0.14\linewidth}|p{0.74\linewidth}|}
\hline
ID & Requirement \\
\hline
FR-01 & Provide a visible and labeled primary button to start night mode. \\
\hline
FR-02 & On activation, transition background from default state to night sky. \\
\hline
FR-03 & Start and display northern-lights animation after transition starts. \\
\hline
FR-04 & Support both pointer click and keyboard activation. \\
\hline
FR-05 & Maintain responsive layout for mobile and desktop viewports. \\
\hline
FR-06 & Respect \texttt{prefers-reduced-motion} by reducing or disabling heavy animation. \\
\hline
\end{longtable}

\section{Non-Functional Requirements}
\begin{longtable}{|p{0.14\linewidth}|p{0.74\linewidth}|}
\hline
ID & Requirement \\
\hline
NFR-01 & Trigger response time should be <= 200 ms on baseline test hardware. \\
\hline
NFR-02 & Achieve Lighthouse accessibility score >= 90 for the MVP page. \\
\hline
NFR-03 & No critical console errors during normal interaction flow. \\
\hline
NFR-04 & Use vanilla HTML/CSS/JS for v1; avoid large runtime libraries. \\
\hline
\end{longtable}

\section{Prioritization}
\subsection{MVP (Must Have)}
FR-01 to FR-06 and NFR-01 to NFR-04.

\subsection{Post-MVP (Could Have)}
\begin{itemize}[leftmargin=*]
  \item Additional theme presets.
  \item Audio effects with user opt-in.
  \item Advanced shader effects if needed.
\end{itemize}

\section{Acceptance Criteria}
MVP is accepted when all must-have requirements are implemented and test evidence is recorded in the test artifacts.

\end{document}
