\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\title{Test Plan: Aurora}
\author{QA Team}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Test Strategy}
\begin{itemize}[leftmargin=*]
  \item Validate requirements from SRS (FR and NFR IDs).
  \item Combine manual exploratory testing with checklist-based validation.
  \item Prioritize interaction, accessibility, performance, and fallback behavior.
\end{itemize}

\section{Scope of Testing}
\subsection{In Scope}
\begin{itemize}[leftmargin=*]
  \item Button activation by pointer and keyboard.
  \item Night transition correctness.
  \item Aurora behavior in video-first mode and canvas fallback mode.
  \item Interactive visual responses (pointer parallax, cursor glow, and button micro-feedback).
  \item Reduced-motion behavior and runtime mode switching.
  \item Responsive layout at representative viewport sizes.
\end{itemize}

\subsection{Out of Scope}
\begin{itemize}[leftmargin=*]
  \item Backend or API testing (none in v1/v1.2).
  \item Legacy browser compatibility testing outside target matrix.
\end{itemize}

\section{Test Environment}
\begin{itemize}[leftmargin=*]
  \item OS: Windows baseline workstation.
  \item Browsers: latest Chrome, Edge, Firefox.
  \item Tools: Browser DevTools, Lighthouse, manual keyboard test.
  \item Media assets under test: \texttt{assets/aurora-loop.webm} and \texttt{assets/aurora-loop.mp4}.
\end{itemize}

\section{Entry and Exit Criteria}
\subsection{Entry}
\begin{itemize}[leftmargin=*]
  \item FR-01 to FR-06 implementation complete.
  \item Video-first runtime integrated with fallback path.
  \item Build deployable in local browser.
\end{itemize}

\subsection{Exit}
\begin{itemize}[leftmargin=*]
  \item All critical and high defects resolved or explicitly deferred.
  \item All must-have test cases pass.
  \item RTM updated with execution status.
\end{itemize}

\section{Execution Snapshot}
\subsection{Baseline (v1.1.0)}
\begin{itemize}[leftmargin=*]
  \item TC-01: Pass
  \item TC-02: Pass
  \item TC-03: Pass
  \item TC-04: Pass (verified)
  \item TC-05: Pass
  \item TC-06: Pass
  \item TC-07: Pass
  \item TC-08: Pass
  \item TC-09: Pass
  \item TC-10: Pass
\end{itemize}

\subsection{v1.2 Revalidation (Current)}
\begin{itemize}[leftmargin=*]
  \item TC-11 to TC-17 defined for realism and interaction validation.
  \item Status: Pending execution (WP-09 in progress).
\end{itemize}

\section{Defect Management}
\begin{itemize}[leftmargin=*]
  \item Severity levels: Critical, High, Medium, Low.
  \item Critical/High must be resolved before release publication.
\end{itemize}

\subsection{Defect Log}
\begin{longtable}{|p{0.16\linewidth}|p{0.26\linewidth}|p{0.20\linewidth}|p{0.28\linewidth}|}
\hline
Defect ID & Related Test & Severity & Status \\
\hline
D-01 & TC-04 keyboard activation inconsistency & Medium & Closed after successful retest on 2026-02-18 \\
\hline
\end{longtable}

\section{Test Schedule}
\begin{longtable}{|p{0.36\linewidth}|p{0.20\linewidth}|p{0.34\linewidth}|}
\hline
Phase & Window & Output \\
\hline
Baseline validation (v1.1.0) & 2026-02-18 to 2026-02-18 & TC-01 to TC-10 completed \\
\hline
v1.2 realism and interaction test design & 2026-02-19 to 2026-02-20 & Finalized TC-11 to TC-17 \\
\hline
v1.2 execution and regression & 2026-02-20 to 2026-03-05 & Pass/fail evidence and defect handling \\
\hline
Release readiness verification & 2026-03-06 to 2026-03-10 & Final pass report for v1.2 candidate \\
\hline
\end{longtable}

\end{document}
