\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}

\title{Test Cases: Aurora}
\author{QA Team}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Test Case Template}
Fields: ID, Requirement ID, Preconditions, Steps, Expected Result, Status.

\section{Functional Test Cases (Baseline)}
\begin{longtable}{|p{0.10\linewidth}|p{0.12\linewidth}|p{0.58\linewidth}|p{0.14\linewidth}|}
\hline
Test ID & Req ID & Expected Result & Status \\
\hline
TC-01 & FR-01 & Primary action button is visible and clearly labeled on initial load. & Pass \\
\hline
TC-02 & FR-02 & Clicking the button transitions scene to night-sky mode. & Pass \\
\hline
TC-03 & FR-03 & Aurora animation starts after activation and remains visible. & Pass \\
\hline
TC-04 & FR-04 & Keyboard activation (Enter/Space) triggers the same transition. & Pass \\
\hline
TC-05 & FR-05 & Layout remains usable on mobile and desktop test sizes. & Pass \\
\hline
TC-06 & FR-06 & Reduced-motion preference lowers or disables heavy motion effects. & Pass \\
\hline
\end{longtable}

\section{Non-Functional Test Cases (Baseline)}
\begin{longtable}{|p{0.10\linewidth}|p{0.12\linewidth}|p{0.58\linewidth}|p{0.14\linewidth}|}
\hline
Test ID & Req ID & Expected Result & Status \\
\hline
TC-07 & NFR-01 & Activation response begins within 200 ms under baseline conditions. & Pass \\
\hline
TC-08 & NFR-02 & Accessibility baseline checks pass target threshold. & Pass \\
\hline
TC-09 & NFR-03 & No heavy runtime animation library is present in v1 bundle. & Pass \\
\hline
TC-10 & NFR-04 & No uncaught errors appear in normal flow console trace. & Pass \\
\hline
\end{longtable}

\section{v1.2 Extension Test Cases (Realism + Interactions)}
\begin{longtable}{|p{0.10\linewidth}|p{0.12\linewidth}|p{0.58\linewidth}|p{0.14\linewidth}|}
\hline
Test ID & Req ID & Expected Result & Status \\
\hline
TC-11 & FR-03 & With valid video assets, activation uses video-first aurora and updates status accordingly. & Pending \\
\hline
TC-12 & FR-03 & If video assets are missing or fail, canvas fallback starts automatically without blocking activation. & Pending \\
\hline
TC-13 & FR-06 & In reduced-motion mode, video path is not used and reduced canvas mode runs. & Pending \\
\hline
TC-14 & NFR-01 & Activation remains within 200 ms median while video-first path is enabled. & Pending \\
\hline
TC-15 & NFR-02 & Accessibility score remains >= 90 and keyboard parity remains intact after realism update. & Pending \\
\hline
TC-16 & FR-05 & Pointer movement drives subtle scene parallax/cursor glow and interaction reset behaves correctly on blur/visibility change. & Pending \\
\hline
TC-17 & FR-06 & Reduced-motion mode suppresses interaction-heavy effects (parallax/ripple/tilt) while preserving activation behavior. & Pending \\
\hline
\end{longtable}

\section{Execution Log}
\begin{itemize}
  \item 2026-02-18: TC-01 passed.
  \item 2026-02-18: TC-02 passed.
  \item 2026-02-18: TC-03 passed.
  \item 2026-02-18: TC-04 failed (keyboard behavior inconsistent in initial implementation).
  \item 2026-02-18: Keyboard activation fix implemented in \texttt{app.js}; retest required for TC-04.
  \item 2026-02-18: TC-04 retest passed and verified.
  \item 2026-02-18: TC-05 passed.
  \item 2026-02-18: TC-06 passed.
  \item 2026-02-18: TC-07 passed.
  \item 2026-02-18: TC-08 passed (Lighthouse accessibility baseline verified).
  \item 2026-02-18: TC-09 passed (vanilla JS dependency constraint verified).
  \item 2026-02-18: TC-10 passed (no uncaught runtime errors observed in normal flow).
  \item 2026-02-18: TC-11 to TC-17 defined for v1.2 realism and interaction runtime; execution pending.
\end{itemize}

\section{Regression Set}
Run TC-01 to TC-17 after each significant animation, media, or interaction change.

\end{document}
