\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\title{Release and Deployment Plan: Aurora}
\author{Project Team}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Release Scope}
\begin{itemize}[leftmargin=*]
  \item Published baseline: \texttt{v1.1.0} includes FR-01 to FR-06 and NFR-01 to NFR-04.
  \item Next target: \texttt{v1.2.0} realism and interaction upgrade (video-first aurora with fallback + interactive effects).
\end{itemize}

\section{Deployment Strategy}
\begin{itemize}[leftmargin=*]
  \item Deployment model: static hosting.
  \item Build output: static HTML/CSS/JS plus media assets.
  \item Target repository: \texttt{https://github.com/Tanvir-Sadi/aurora}.
\end{itemize}

\section{Release Checklist Result (Published Baseline)}
\begin{itemize}[leftmargin=*]
  \item Completed: Test cases TC-01 to TC-10 executed and recorded as pass.
  \item Completed: No open critical or high defects.
  \item Completed: Lighthouse performance and accessibility checks captured.
  \item Completed: Reduced-motion behavior verified.
  \item Completed: SDLC docs synchronized with implementation baseline.
\end{itemize}

\section{Published Release Record}
\begin{itemize}[leftmargin=*]
  \item Release date: 2026-02-18.
  \item Published tag: \texttt{v1.1.0}.
  \item Source branch: \texttt{main}.
  \item Release commit: \texttt{5665d06}.
\end{itemize}

\section{v1.2 Candidate Checklist (Current)}
\begin{itemize}[leftmargin=*]
  \item Completed: Realism implementation delivered in runtime (B-01 to B-03).
  \item Completed: Interaction layer delivered (pointer parallax, cursor glow, button micro-feedback).
  \item Completed: Media assets added (\texttt{assets/aurora-loop.webm}, \texttt{assets/aurora-loop.mp4}).
  \item Pending: Execute TC-11 to TC-17 and capture evidence.
  \item Pending: Confirm performance/accessibility guardrails after realism and interaction updates.
  \item Pending: Prepare \texttt{v1.2.0} release notes and publish tag.
\end{itemize}

\section{Rollback Plan}
\begin{itemize}[leftmargin=*]
  \item Keep previous deployment artifact available.
  \item Revert to prior stable release tag (\texttt{v1.1.0}) if needed.
  \item Publish rollback note with issue summary.
\end{itemize}

\section{Go-Live Validation}
\begin{itemize}[leftmargin=*]
  \item \texttt{v1.1.0}: Production activation flow validated on Chrome, Edge, and Firefox.
  \item \texttt{v1.2.0}: Validation pending completion of TC-11 to TC-17.
\end{itemize}

\section{Release Ownership}
Release manager: Tanvir Sadi.

\end{document}
