\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\title{Operations and Maintenance Plan: Aurora}
\author{Project Team}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Operational Model}
Aurora is a static frontend application with lightweight operational needs.

\section{Current Production Baseline}
\begin{itemize}[leftmargin=*]
  \item Current version: \texttt{v1.1.0}.
  \item Release date: 2026-02-18.
  \item Hosting model: static site from repository artifacts.
  \item Runtime rendering: canvas aurora in baseline release, with v1.2 introducing video-first mode and interactive visual effects.
  \item Known critical/high production defects at release: none.
\end{itemize}

\section{Monitoring and Alerting}
\begin{itemize}[leftmargin=*]
  \item Uptime check on production URL.
  \item Basic client-side error review from browser/session logs when available.
  \item Periodic Lighthouse checks after major changes.
  \item Confirm media delivery success for \texttt{assets/aurora-loop.webm} and \texttt{assets/aurora-loop.mp4} after deploy.
  \item Spot-check pointer and keyboard interaction flows after each deployment.
\end{itemize}

\section{Incident and Problem Management}
\begin{itemize}[leftmargin=*]
  \item Classify incidents by severity: Critical, High, Medium, Low.
  \item Critical issues (site unavailable or broken core interaction) require immediate rollback or hotfix.
  \item If video playback fails broadly, switch to canvas fallback path and treat as High severity defect.
  \item If interaction effects degrade usability or accessibility, disable/rollback the effect layer and track root cause.
  \item Record root cause and preventive action in follow-up notes.
\end{itemize}

\section{Backup and Recovery}
\begin{itemize}[leftmargin=*]
  \item Keep previous deploy artifacts or release tags.
  \item Recovery path is redeploying last known stable static bundle.
  \item Primary rollback tag for next release candidate: \texttt{v1.1.0}.
\end{itemize}

\section{Patch and Upgrade Plan}
\begin{itemize}[leftmargin=*]
  \item Weekly review window for improvements and fixes.
  \item Re-run regression set for every visible animation, media, or interaction change.
  \item For v1.2, close TC-11 to TC-17 before release publication.
  \item Revisit architecture only if realism/performance constraints cannot be met with current approach.
\end{itemize}

\section{Support SLA (Project-Level)}
\begin{itemize}[leftmargin=*]
  \item Critical issue response target: within 24 hours.
  \item High issue response target: within 48 hours.
\end{itemize}

\end{document}
