\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{array}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}

\title{Post-Implementation Review (PIR): Aurora}
\author{Project Team}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Current Review Status}
\begin{itemize}[leftmargin=*]
  \item Release status: Released.
  \item Release version: \texttt{v1.1.0}.
  \item Release date: 2026-02-18.
\end{itemize}

\section{Review Inputs Used}
\begin{itemize}[leftmargin=*]
  \item RTM evidence confirms FR-01 to FR-06 and NFR-01 to NFR-04 as pass for baseline release.
  \item Test execution log in \texttt{07\_test\_cases.tex} with TC-01 to TC-10 pass.
  \item Lighthouse evidence and reduced-motion verification captured during QA.
\end{itemize}

\section{Objectives vs Outcomes}
\begin{itemize}[leftmargin=*]
  \item Objective: Deliver interactive night-sky activation and aurora animation using vanilla JS.
  \item Outcome: Achieved in MVP release \texttt{v1.1.0}.
  \item Objective: Complete baseline SDLC documentation and traceability.
  \item Outcome: Achieved with synchronized Plan, SRS, SDS, Test, RTM, and release docs.
\end{itemize}

\section{What Went Well}
\begin{itemize}[leftmargin=*]
  \item Requirement traceability remained consistent from SRS through RTM.
  \item Accessibility and reduced-motion behavior were included and validated before release.
  \item Defect D-01 (keyboard activation inconsistency) was closed before go-live.
\end{itemize}

\section{What Did Not Go Well}
\begin{itemize}[leftmargin=*]
  \item Keyboard activation behavior required a correction cycle during testing.
  \item Release readiness tracking required multiple manual sync steps across documents.
\end{itemize}

\section{Lessons Learned}
\begin{itemize}[leftmargin=*]
  \item Run keyboard and reduced-motion checks earlier in implementation sprints.
  \item Keep test evidence updates batched with code changes to reduce drift.
  \item Keep release checklist result recorded immediately after tag publication.
\end{itemize}

\section{Action Items}
\small
\begin{longtable}{|>{\raggedright\arraybackslash}p{0.08\linewidth}|>{\raggedright\arraybackslash}p{0.26\linewidth}|>{\raggedright\arraybackslash}p{0.11\linewidth}|>{\raggedright\arraybackslash}p{0.11\linewidth}|>{\raggedright\arraybackslash}p{0.14\linewidth}|>{\raggedright\arraybackslash}p{0.22\linewidth}|}
\hline
ID & Action Item & Owner & Due Date & Status & Evidence \\
\hline
A-01 & Add a lightweight scripted release notes template for next release cycle & Tanvir & 2026-03-10 & Completed (2026-02-18) & \url{RELEASE_NOTES_TEMPLATE.md}; \url{scripts/new-release-notes.ps1} \\
\hline
A-02 & Define v1.2 backlog with realistic aurora targets, UX polish scope, and performance guardrails & Tanvir & 2026-03-10 & Completed (2026-02-18) & \url{latex/sdlc/12_v1_2_backlog.tex} \\
\hline
\end{longtable}
\normalsize

\section{Follow-Up Status (v1.2 Program)}
\begin{itemize}[leftmargin=*]
  \item B-01 to B-03 implementation delivered (video-first realism runtime with fallback).
  \item B-05 interaction/accessibility polish implementation delivered (parallax/cursor glow/button feedback).
  \item Validation for TC-11 to TC-17 is pending under WP-09.
  \item Next PIR update should be issued after \texttt{v1.2.0} release decision.
\end{itemize}

\end{document}
