\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\title{v1.2 Backlog and Target Definition: Aurora}
\author{Project Team}
\date{2026-02-18}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Purpose}
This document defines the prioritized backlog for v1.2 and measurable quality targets aligned with PIR action item A-02.

\section{Baseline and Scope}
\begin{itemize}[leftmargin=*]
  \item Baseline release: \texttt{v1.1.0}.
  \item Scope type: realistic aurora rendering, interaction polish, and release process improvements.
  \item Constraint: keep implementation lightweight and maintain accessibility baseline.
\end{itemize}

\section{Measurable Targets (v1.2)}
\begin{longtable}{|p{0.14\linewidth}|p{0.30\linewidth}|p{0.22\linewidth}|p{0.24\linewidth}|}
\hline
Target ID & Metric & Current Baseline & v1.2 Target \\
\hline
RL-01 & Aurora realism fidelity & Basic layered wave look & Multi-layer curtain effect with vertical variation and depth haze \\
\hline
RL-02 & Color realism & Fixed palette blend & Dynamic gradient flow (green/cyan dominant with subtle magenta accents) \\
\hline
RL-03 & Motion naturalness & Repeating wave movement & Less repetitive drift with noise-driven phase variation \\
\hline
UX-02 & Interaction polish & Static scene feedback & Subtle pointer parallax and button micro-feedback without usability regressions \\
\hline
PT-01 & Lighthouse Performance score & 94 & >= 93 while realism updates are enabled \\
\hline
PT-02 & Activation response (NFR-01 path) & <= 200 ms (pass) & <= 200 ms median on baseline test machine \\
\hline
UX-01 & Accessibility stability & Baseline pass & Preserve >= 100 Lighthouse accessibility and keyboard parity \\
\hline
OPS-01 & Release documentation speed & Manual template edits & Scripted notes generation in < 2 minutes \\
\hline
\end{longtable}

\section{Prioritized Backlog}
\begin{longtable}{|p{0.10\linewidth}|p{0.36\linewidth}|p{0.10\linewidth}|p{0.11\linewidth}|p{0.17\linewidth}|p{0.11\linewidth}|}
\hline
ID & Backlog Item & Priority & Type & Acceptance Criteria & Status \\
\hline
B-01 & Implement multi-layer, noise-modulated aurora curtains for realistic shape dynamics. & High & Visual Realism & At least four distinct moving layers with non-repetitive contour behavior. & Implemented (QA pending) \\
\hline
B-02 & Add vertical light-veil variation and atmospheric haze to increase depth perception. & High & Visual Realism & Visible depth separation and soft upper-atmosphere haze in active mode. & Implemented (QA pending) \\
\hline
B-03 & Improve color blending model for realistic aurora transitions and glow falloff. & High & Visual Realism & Smooth color transitions without banding or harsh clipping artifacts. & Implemented (QA pending) \\
\hline
B-04 & Introduce optional visual tuning controls for animation intensity. & Medium & UX & User can adjust intensity without breaking reduced-motion behavior. & Planned \\
\hline
B-05 & Improve focus-visible styling and keyboard feedback consistency. & Medium & Accessibility & Keyboard-only flow remains fully operable and obvious, with consistent interaction feedback. & Implemented (QA pending) \\
\hline
B-06 & Add scripted release notes generation to release process. & Medium & Operations & \texttt{new-release-notes.ps1} generates usable notes file successfully. & Completed \\
\hline
B-07 & Add post-release smoke checklist to release package. & Low & Operations & Smoke checklist executed and documented per release. & Planned \\
\hline
\end{longtable}

\section{Implementation Status Snapshot (2026-02-18)}
\begin{itemize}[leftmargin=*]
  \item B-01/B-02/B-03 delivered as video-first runtime with canvas fallback in \texttt{index.html}, \texttt{app.js}, and \texttt{aurora.js}.
  \item Interaction layer delivered in \texttt{app.js}/\texttt{styles.css}: pointer parallax, cursor glow, and button micro-feedback.
  \item Realistic loop assets generated and stored as \texttt{assets/aurora-loop.webm} and \texttt{assets/aurora-loop.mp4}.
  \item Asset generation workflow captured in \texttt{scripts/generate-aurora-video.py}.
  \item Remaining work for implemented items: objective validation against RL-01 to RL-03, UX-02, and PT/UX guardrails.
  \item Next coding focus after validation: B-04 and B-07.
\end{itemize}

\section{Execution Plan}
\begin{itemize}[leftmargin=*]
  \item Sprint window: 2026-02-19 to 2026-03-10.
  \item Milestone 1: Realism implementation (B-01, B-02, B-03) - delivered.
  \item Milestone 2: Interaction/accessibility polish (B-05) - delivered pending QA.
  \item Milestone 3: Validation and tuning pass (TC-11 to TC-17).
  \item Milestone 4: Remaining UX and operations improvements (B-04, B-07).
\end{itemize}

\section{Validation Plan for v1.2}
\begin{itemize}[leftmargin=*]
  \item Re-run TC-01 to TC-10 and execute TC-11 to TC-17 for realism and interaction behavior.
  \item Capture Lighthouse report evidence for performance and accessibility guardrails.
  \item Update RTM and release notes with final pass/fail evidence.
\end{itemize}

\end{document}
